%-------------------------------------------------------------------------------
% Packages and config
%-------------------------------------------------------------------------------
\documentclass[11pt,letterpaper,sans]{moderncv}

% moderncv themes
\moderncvstyle[right]{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}

\input{functions.tex}

%-------------------------------------------------------------------------------
% personal data

\name{Muhammed Mücahid}{Benlioğlu}
\title{Curriculum Vitae}
\address{1390 Northside Drive NW, Apt.1509}{Atlanta, GA, USA}{} % TODO - update address
\phone[mobile]{+1~(404)~960~8803}
\phone[mobile]{+90~(530)~953~0966}
\email{m.mucahidbenlioglu@gmail.com}
\social[linkedin]{mbenlioglu}
\social[github]{mbenlioglu}
\homepage{mucahidbenlioglu.com}

\begin{document}
\makecvtitle
\vspace*{-10mm}     % Adjust spacing

%-------------------------------------------------------------------------------
% Education

\tightsection{Education}
%\cventry{\yearabove{August}{2019}-- Now}{Georgia Institute of Technology}{PhD}
\cventry{\dates[06.2019-12.2020]}{Georgia Institute of Technology}{PhD}
    {Atlanta, GA, USA}{\small{\textit{\textbf{Computational Science and Engineering}}}}{
        \begin{itemize}
            \item Advisor: Prof. Dr. Ümit Çatalyürek. Research Area: \textit{High
            Performance Computing}
        \end{itemize}
    }
\cventry{\dates[09.2013-06.2018]}{Sabanci University}{Bachelor of Science}
    {Istanbul, Turkey}{\textit{\textbf{Computer Science and Engineering}}}{
        \begin{itemize}
            \item With Sakip Sabanci High Success Scholarship. GPA: 3.83/4.0,
            PGPA: 3.87/4.0
        \end{itemize}}
%-------------------------------------------------------------------------------
% Experience

\tightsection{Work Experience}
\cventry{\dates[06.2017-09.2017]}{Proente}{Software Engineer}{Istanbul, Turkey}
    {\bluelink{proente.com/en}}{
        \begin{itemize}
        \item Full stack development and deployment of the data analytics and visualization
        software, Prowmes.
        \end{itemize}
    }
\cventry{\dates[06.2016-09.2016]}{SemperTech}{Internship, Software Engineer}{Istanbul, Turkey}
    {\bluelink{semper-tech.com/en}}{
        \begin{itemize}
        \item Designed and developed full-stack mobile applications having RESTful
        web service, push notifications, data analysis and graphical visualization.
        \end{itemize}
    }

\tightsection{Teaching Experience}
\cventry{\dates[02.2018-05.2018]}{CS Essentials Workshop Series}{Sabanci University}
    {Istanbul, Turkey}{}{
        \begin{itemize}
        \item \textit{Co-designed} and \textit{instructed} series of workshops covering
        fundamental CS practices and tools such as Linux (terminal), git VCS NoSQL/Graph
        databases and Python. \github{CSEssentialsWorkshops}{}
        \end{itemize}
    }
\cventry{\dates[09.2016-05.2017]}{Undergraduate Teaching Assistant}{Sabanci University}
    {Istanbul, Turkey}{\footnotesize{\textbf{\emph{MySQL, C++}}}}{
        \begin{itemize}
        \item Prepared HW/project documents and solutions, supervised students. \textit{Database Systems, Operating Systems}
        \end{itemize}
    }

%-------------------------------------------------------------------------------
% Publications

%%\renewcommand{\refname}{Articles}     % Change name to 'Articles'
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}

%-------------------------------------------------------------------------------
% Selected Projects

\tightsection{Selected Projects}
\cventry{\dates[09.2017-02.2018]}{Crycur}{Sabanci University}{Istanbul, Turkey}{\benkos{crycur}}{
    \begin{itemize}
        \item Designed and implemented a CLI tool that has needed cryptographic functions
        for a simulated cryptocurrency.
    \end{itemize}}
\cventry{\dates[09.2016-09.2017]}{Differential Privacy Framework for Movie Recommendation Systems}
    {\small{Sabanci University}}{\small{Istanbul}}{}{
        \begin{itemize}
            \item Researched and implemented a movie recommendation system using
            differential privacy methods.
            \item Further information and source code: \benkos{pymovielens}
        \end{itemize}
    }

%-------------------------------------------------------------------------------
% Voluntary

\tightsection{Voluntary Works}
\cventry{2014--2015}{Civic Involvement Projects}{Sabanci University}{Istanbul, Turkey}{}{
    \begin{itemize}
        \item Visited and made activities with elderly people in two different
        retirement homes in Istanbul.
    \end{itemize}}

%-------------------------------------------------------------------------------
% Skills & Hobbies etc.

\tightsection{Computer \& Software Skills}
\cvlistdoubleitem{C/C++, Python, Neo4j~~~~~~\skill{5}}{Git, Linux, Docker, MySQL~\skill{5}}
\cvlistdoubleitem{Android, Java, JS, HTML~~~\skill{4}}{C\#, PHP~~~~~~~~~~~~~~~~~~~~~~~\skill{2}}
%\begin{cvcolumns}
%    \cvcolumn{}{C/C++}
%\end{cvcolumns}

\tightsection{Personal Skills}
\cvdoubleitem{\textbf{Languages:}}{Turkish(Native), English(Advanced)}
	{\textbf{Hobies:}}{Archery, Chess, Tabletop games}
%\cvitem{Hobies}{Archery, Chess, Tabletop games}

%-------------------------------------------------------------------------------
% References

\tightsection{References}
\cventry{\small \textbf{Prof. Dr. Ümit Çatalyürek}}{Assoc. Chair}{Computational
    Science and Engineering}{\textbf{Georiga Institue of Technology}}{}{
    \begin{itemize}
        \item \textbf{Email:} \href{mailto:umit@gatech.edu}{umit@gatech.edu} --
        \textbf{Phone:} +1 (404) 894-2592
    \end{itemize}}
\cventry{\small \textbf{Prof. Dr. Yücel Saygın}}{Faculty Member}{Computer Science
    and Engineering}{\textbf{Sabanci University}}{}{
    \begin{itemize}
        \item \textbf{Email:} \href{mailto:ysaygin@sabanciuniv.edu}{ysaygin@sabanciuniv.edu} --
        \textbf{Phone:} +90 (216) 483-9576
    \end{itemize}}

\clearpage
\end{document}
